Efficient ancestry and mutation simulation with msprime 1.0

### 2021-11-18 response-to-reviewers.tex

\item All plots now contain data markers to help show where the data
points are and to distinguish the lines from each other.

\item All plots state they are running ``sim\_ancestry`` or ``sim\_mutations``.

\item Stated explicitly whether samples are haploid or diploid in the
figure captions, and updated axis labels also.

\item All figures now show the time averaged across replicates.

@@

\begin{point}
Figure 5
I suggest including the absolute Ne and gc rates be included in the legend, in
addition to the scaled rate.
\end{point}

\begin{reply}
We avoided included the absolute values here in order to make the comparison
between the simulators as simple as possible (since SimBac and FastSimBac
require scaled inputs). Since the values we use aren't precisely the estimates
for E.~coli (we rounded some values for simplicity), it would probably
be misleading to include some Ne and gc rates that are consistent with the
scaled value we used, but not equal to the actual E.~coli estimates, and
we would therefore prefer not to include them.
\end{reply}

\begin{point}
Figure 7
Why is an order of magnitude lower recombination rate used here than in other
examples? This choice seems arbitrary and makes it difficult to relate these
benchmarks results to any others in the paper. Samples are diploid or haploid?
I would suggest the absolute Ne and s rates be included in the legend, in
addition to the scaled rate.
\end{point}

\begin{reply}
We have redone this figure to use the same recombination rate and population
sizes as the rest of the paper, clarified that samples are diploid, given
results in terms of the average per replicate and generally made the plot
as close to the others as possible.
\end{reply}

### 2021-11-18 paper.tex

\begin{figure}
\begin{center}
\includegraphics{figures/sweeps-perf}
\end{center}
\caption{\label{fig-selection-perf}Comparison of selective sweep simulation
performance in \msprime\ and \discoal\ (Intel Xeon E5-2680 CPU).
We report the average CPU time and maximum memory usage when simulating 3
replicates for 200 haploid samples in a model
with a single selective sweep in its history where the beneficial
allele had a selection coefficient of $s=0.05$,
a per-base recombination rate of $10^{-8}$, population size of $N=10^4$,
and sequence length varying from 100kb--3000kb.}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics{figures/sweeps-perf}
\end{center}
\caption{\label{fig-selection-perf}Comparison of selective sweep simulation
performance in \msprime\ (\texttt{sim\_ancestry}) and \discoal\ (Intel Xeon Gold 6148 CPU).
We report the average CPU time and maximum memory usage when simulating 3
replicates for 100 diploid samples in a model
with a single selective sweep in its history, where the beneficial
allele had a selection coefficient of $s=0.05$,
a per-base recombination rate of $10^{-8}$, population size of $N=10^4$,
and sequence length varying from 100kb--3000kb.}
\end{figure}
